\hh{PCMS Web Client User Guide}

\ifdefined\online
    \input{handbook-web-login.tex}
\else
    \input{handbook-spb-login.tex}
\fi

The \emph{Information} page contains contest information and messages
sent by the Jury.
During the Contest you will receive messages from the Jury with the results
of your runs and clarifications.
Incoming messages will be listed on this page.
You can always read all your previous messages in this list.

The \emph{Monitor} page contains the standings table.
Teams are displayed as the rows of the table, ordered by team's rank.
Problems correspond to the table columns.
The intersection of team and problem contains information about team's
result for that problem and the time of the first accepted run on this
problem, measured in minutes.

Possible results are:
\nopagebreak
{
\makeatletter
\@beginparpenalty=10000
\makeatother
\begin{shortitems}
    \itemindent=1cm
    \item[``\texttt{.}''] --- team has no runs for this problem;
    \item[``\texttt{+}''] --- team has solved this problem, the first
        run was successful;
    \item[``\texttt{+k}''] --- team has solved this problem after
        $k$ unsuccessful runs;
    \item[``\texttt{-k}''] --- team has $k$ unsuccessful runs for this
        problem.
\end{shortitems}
}

To submit a program for evaluation, you should select the \emph{Submit} page.
Choose the problem you have solved from the \emph{Problem} combo box and
the language of your solution from the \emph{Language} combo box.
Press the \emph{Choose File} button and choose the file that contains your solution,
then press the \emph{Submit solution} button.
You will see a page, confirming that your solution was successfully sent
to the server for evaluation.
Your solution will appear in the \emph{Runs} page.
The evaluation result will appear on this page when solution is evaluated.
You may solve other problems while waiting for the result.

To submit a clarification request, you should select the \emph{Questions} page.
Choose the problem you have the clarification request for from the \emph{Problem}
combo box and type your clarification request in the \emph{Question} field,
then press the \emph{Ask a question} button.
The list of already asked questions and corresponding answers are displayed
on the same page.

To get the samples for all contest problems, select the \emph{Files} page. There
you will find an archive for downloading.
